\section{Introduction}
	\subsection{Purpose - Description of the Problem}
	\paragraph*{}This document is the Requirement Analysis and Specification Document (RASD) of a system, called myTaxiService, used to manage a taxi service in a city. The main goals of this document are to: describe the system in terms of functional and non-funcional requirements, specify the requirements and the costrains, and specify how the system will beheave in its application, once that it is deployed. This document is meant to be read by the developers of the software, but also by the customer, to be sure that all what he asks is well defined and corresponds to what is going to be developed; this document, hence, can be used as a contract between the customer and the developers.
		
	\subsection{Scope - Goals}
	\paragraph*{}The scope of the system is to manage taxis around the city. The city is divided in zone of 2 squarekilometers and for each zone the system defines a queue based on the free taxis in that specific zone. A user can require a taxi ride from a zone, but can also book one for another moment.
	
	\subsection{Actors}
	\begin{itemize}
		\item Users: users can request a taxi ride or book one, using the mobile app or the website.
		\item Taxis: taxis work for a taxi company and provide the service to the users by transporting them to their destination.
	\end{itemize}
	\subsection{Definitions, acronyms and abbreviations}
		\subsubsection{Definitions}
		\begin{itemize}
			\item myTaxiService: the system described in this document
			\item User: someone who uses the services offered by myTaxiService
			\item Taxi: entity composed by the taxi driver and the taxi car that transports the users
		\end{itemize}
		\subsubsection{Acronyms}
		\begin{itemize}
			\item a
		\end{itemize}
		\subsubsection{Abbreviations}
		\begin{itemize}
			\item b
		\end{itemize}
	\subsection{Reference Documents}
	\begin{itemize}
		\item IEEE Std 830-1998 (Revision of IEEE Std 830-1993) document available on the \url{http://standards.ieee.org/} website
		\item Assignment 1 from the \emph{Assignment 1 and 2.pdf} file on BeeP university platform
	\end{itemize}
	\subsection{Overview}
		\paragraph*{}Section 2 and 3 of this document provide a syntethic but exhaustive description of the product that will be developed.		
		\paragraph*{}Specifically section 2 provides a description of the general factors that affect the product and the requirements' background, specifying the product perspective, user characteristics product functions, product constrains and assumptions and dependecies made to write this document.
		\paragraph*{}Section 3 instead focuses on the specific requirements of the product listing all the external, hardware, software and communication interfaces if any, functional and non-functional requirements, the description of \emph{The World and The Machine} graph, listing some scenarios of interest in which the product will operate and other requirements that do not belong to any of the previous category. 
	
	