\section{Introduction}
\subsection{Purpose}
	This document is the Project Plan of a system, called myTaxiService, used to manage  a taxi service in a city. The main goal of this document is to estimate the overall cost and define the risk of the project and system.
\subsection{Scope}
	The scope of this system is to manage taxis in a city. A town is divided in zone of 2 square kilometers and, for each zone, the system defines a queue, composed by the identifier, which is the vehicle plate, of free taxis in that specific zone. A user can require a taxi ride from a zone, but he/she can also book one for another moment, using the web application or the mobile one. Furthermore, about long-term reservations, after the user has created one, he/she is able to modify the date or the hour or both of his/her booking, and he/she can delete it. 
\subsection{Acronyms and abbreviations}
	\subsubsection{Acronyms}
		\begin{itemize}
			\item FP: Function Points;
			\item ILF: Internal Logic File;
			\item EIF: External Interface File;
			\item EO: External Output;
			\item UFP: Unadjusted Function Points;
			\item JEE: Java Enterprise Edition.
		\end{itemize}
	\subsubsection{Abbreviations}
		\begin{itemize}
			\item EInput: External Input;
			\item EInquiry: External Inquiry;
			\item SLOC: Source Line of Code;
			\item E: Exponent derived from Scale Drivers;
			\item EAF: Effort Adjustment Factor derived from Cost Drivers;
			\item PREC: Precedentedness;
			\item FLEX: Development Flexibility;
			\item RESL: Risk Resolution;
			\item TEAM: Team Cohesion;
			\item PMAT: Process Maturity;
			\item RELY: Required Software Reliability;
			\item DATA: Database Size;
			\item CPLX: Product Complexity;
			\item RUSE: Developed for Reusability;
			\item DOCU: Documentation Match to Life-Cycle Needs;
			\item TIME: Execution Time Constraint;
			\item STOR: Main Storage Constraint;
			\item PVOL: Platform Volatility;
			\item ACAP: Analyst Capability;
			\item PCAP: Programmer Capability;
			\item PCON: Personnel Continuity;
			\item APEX: Application Experience;
			\item PLEX: Platform Experience;
			\item LTEX: Language and Tool Experience;
			\item TOOL: Use of Software Tools;
			\item SITE: Multisite Development;
			\item SCED: Required Development Schedule.
		\end{itemize}
\subsection{Reference Documents}
	To redact this document, we used the following other documents as references:
	\begin{itemize}
		\item Design Document from previous delivery
		\item \emph{Cost Estimation.pptx} slides from BeeP site
	\end{itemize}